Methodology for Assessing the State of the Practice for Domain X

### 2020-08-20 StateOfPractice/Methodology/Methodology.tex
further revisions to overview of steps in assessing quality of the domain software; moved Meeting Agenda files to Methodology folder

\begin{enumerate}
\item Start with state of practice research questions.
\item Identify domain.  (Provide criteria on a candidate domain.)
\item Identify list of candidate software in the domain.  (Section~\ref{SecIdentifyCandSoft})
\item \emph{Domain Expert}: Vet domain software list.  
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})
\item \emph{Domain Expert}: Vet domain analysis
\item Measure using ``shallow'' measurement template.
\item Empirical measures.
\item Use AHP process to rank the software.  Tool for estimating AHP results?
  Tool for ranking and sorting by various criteria?  Conditional formula to
  assess software within each measure, or just use opinion of measurer?
\item Identify short list for deeper exploration.
\item \emph{Domain Expert}: vet AHP ranking and short list.
\item With short list:
\begin{enumerate}
\item Survey developers
\item Usability experiments
\item Performance benchmarks
\item Maintainability experiments
\end{enumerate}
\item Compare shallow and deep measures and ranking
\item Answers for research questions.
\end{enumerate}

@@

\section{Identify Candidate Software} \label{SecIdentifyCandSoft}

\begin{enumerate}
\item Must be open source.
\item Must have GitHub repository.
\end{enumerate}

>>>>

\begin{enumerate}
\item Start with state of practice research questions.\pmi{add link to above section}
\item Identify the domain.  (Provide criteria on a candidate domain.) \pmi{as an example what criteria? Do we need to add a section below explaining this?}
\item \emph{Domain Expert}: Create a top ten list of software packages in the domain. \pmi{The details of this will be specified in the Meeting Agenda, so link to that section}
\item Brief the Domain Expert on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments.\pmi{Link this to Meeting Agenda, and create a small summary below; Reword or remove anything from this sentence?}
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be completed}
\item Preliminary filter of software packages list. \pmi{Add section below; Judge on professionalism, available documentation, status, availability of source code}
\item \emph{Domain Expert}: Review domain software list. \pmi{any comments on this? Does this need a section below? Link to appropriate section of Meeting Agenda?}
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be completed}
\item \emph{Domain Expert}: Vet domain analysis.\pmi{This is currently not listed in Meeting Agenda and was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda and link it from here}
\item Gather source code and documentation for each prospective software package.
\item Collect Empirical measures. \pmi{To do: Link to below and edit the section}
\item Measure using ``shallow'' measurement template. \pmi{Add section below and link to actual template}
\item Use AHP process to rank the software packages. \pmi{Link to below section (which needs to be edited) outlining the tool we used, and link the below section to the AHP README file}
\item Identify a short list of five software packages for deeper exploration according to the AHP rankings of the shallow measurements.
\item \emph{Domain Expert}: vet AHP ranking and short list.\pmi{Currently not listed in Meeting Agenda, add it and link to it? ...or is this redundant considering they have made a top ten list and have already vetted the original prospective list (both of these latter Domain Expert actions are listed in the Meeting Agenda)?}
\item With short list:
\begin{enumerate}
\item Survey developers \pmi{To do: Link to survey; Add brief below?}
\item Usability experiments \pmi{Link to section below; link to any other document?}
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: this is still in consideration}
\end{enumerate}
\item Rank short list using pairwise comparison of shortlist results.\pmi{Add section below? Link to another doc?}
\item Compare shallow and deep measures and ranking.\pmi{Add section below? Link to another doc? Anything specific to consider when comparing?}
\item Document answers for research questions.
\end{enumerate}

@@

\section{How to Identify Candidate Software} \label{SecIdentifyCandSoft}
\pmi{outline here how to find such a list}
\begin{enumerate}
\item Must have viewable source code.
\item Ideally have a git repository. \pmi{Not all of mine had this..}
\end{enumerate}
